Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-06 paper.tex
ispell pasado

The power of current cloud vendors is based on the use 
of Virtual Machines (VM) which  
emulates a physical node with its own 
cpus, storage, network interconnection, OS and GPU. 
However, to provide a VM with GPUs means
that the guest host must be equipped with at least one GPU, and
once it has been assigned to an instance, no other VM can use
it. Therefore, the number of VM that are allowed to use a GPU is 
limited by the number of the installed devices. This lack of 
flexibility is also noticed in the cluster configurations, where 
depending on the users’ necessities, 
two approaches to introduce GPGPU computation can be determined:
the conservative, to have a lot of hosts with GPUs to be
ensured that you are likely to satisfy all the requests; or a
more daring approach, where you will count with some GPU-
enabled nodes hoping not to arrive a large burst of requests
so the cluster would run out of GPU resources.

The use of a virtualization technology such as {rCUDA} adds 
the desired flexibility because this software detachs the GPUs 
from the nodes where they are installed allowing all nodes in a cluster 
not only use them as if they were local but also to share them 
achieving a higher utilization rate and reducing the idle status time.

>>>>

The power of current cloud vendors is based on the use 
of Virtual Machines (VM) which  
emulates a physical node with its own 
CPUs, storage, network interconnection, OS and GPU. 
However, to provide a VM with GPUs means
that the guest host must be equipped with at least one GPU, and
once it has been assigned to an instance, no other VM can use
it. Therefore, the number of VM that are allowed to use a GPU is 
limited by the number of the installed devices. This lack of 
flexibility is also noticed in the cluster configurations, where 
depending on the users’ necessities, 
two approaches to introduce GPGPU computation can be determined:
the conservative, to have a lot of hosts with GPUs to be
ensured that you are likely to satisfy all the requests; or a
more daring approach, where you will count with some GPU-
enabled nodes hoping not to arrive a large burst of requests
so the cluster would run out of GPU resources.

The use of a virtualization technology such as {rCUDA} adds 
the desired flexibility because this software detaches the GPUs 
from the nodes where they are installed allowing all nodes in a cluster 
not only use them as if they were local but also to share them 
achieving a higher utilization rate and reducing the idle status time.
